---
title: "Publications and Presentations"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## **Publications**

**PUBLISHED:** 

1.	Gray MJ, Spatz JA, **Carter ED**, Miller DL. Poor Biosecurity Could Lead to Disease Outbreaks in Animal Populations. 2018. PLoS ONE (in press). 

2.	Goodman RM. **Carter ED**. 2017. Survey of Hepetofauna on the Campus of Hampden-Sydney Collece Prince Edward County, Virginia. Catesbeiana 32:2

3.	**Carter ED**. Goodman RM. 2014. Storeria dekayi dekayi (Northern Brown Snake). County record. Catesbeiana 34:1.

**IN REVIEW:**
1.	Goodman RM. **Carter ED**, Hargadon KM. Infection of Ranavirus in Eastern Fence Lizards and Eastern Box Turtles in Central Virginia. Northeastern Naturalist. 

2.	Cusaac JPW, **Carter ED**, Woodhams DC, Robert J, Spatz JA, Howard JL, Lillard C, Graham AW, Hill RD, Reinsch S, McGinnity D, Reeves B, Bemis D, Wilkes RP, Hopkins WB, Waltzek TB, Miller DL, Gray MJ. Interactive Effects of Herbicide and Emerging Amphibian Pathogens in Eastern Hellbender. EcoHealth.

3.	Peace A, O’Regan SM, Spatz JA, Reilly PN, Hill RD, **Carter ED**, Wilkes RP, Waltzek TB, Miller DL, Gray MJ. Dominant transmission pathways depend on population size for a highly virulent, chimeric pathogen. Oikos.

**IN PREPARATION:**
1.	Drought and ranavirus interact to negatively impact wood frogs in the Great Smoky Mountains National Park. Target Journal =  Copeia.

2.	Tolerance of North American Amphibian Species to Batrachochytrium salamandrivorans infections.  Target journal = Proceedings of the National Academy of Sciences (USA). 

3.	Conservation risk of Batrachochytrium salamandrivorans to endemic brook salamanders. Target Journal = Conservation Biology. 

4.	Potential Role of North American Newt Species in the emergence of Batrachochytrium salamandrivorans. Target Journal = Nature. 

5.	Estimating Batrachochytrium salamandrivorans zoospore viability using flow cytometry. Target Journal = Diseases of Aquatic Organisms. 

##**Presentations**

**Lead Presenter:**

1.	**Carter ED**, Gray MJ, Spatz JA, Miller DL. 2018. Interaction of hydroperiod and ranavirus leading to possible amphibian population declines in Great Smoky Mountains National Park. Southeast Partners in Amphibian and Reptile Conservation Helen, GA. (Oral Presentation).
2.	**Carter ED**, Gray MJ, Spatz JA, Miller DL. 2017. Interaction of hydroperiod and ranavirus leading to possible amphibian population declines in Great Smoky Mountains National Park. Southeastern Association of Fish and Wildlife Agencies Louisville, KY (Oral Presentation).
3.	**Carter ED**. 2017. Conservation risk of Batrachochytrium salamandrivorans to endemic brook salamanders. Northeast Partners in Amphibian and Reptile Conservation, Pembroke, VA (Poster).
4.	**Carter ED**. 2017. Gray MJ, Spatz JA, Miller DL, Interaction of hydroperiod and ranavirus leading to possible amphibian population declines in Great Smoky Mountains National Park. Northeast Partners in Amphibian and Reptile Conservation, Pembroke, VA (Poster).
5.	**Carter ED**. 2017. Gray MJ, Spatz JA, Miller DL, Interaction of hydroperiod and ranavirus leading to possible amphibian population declines in Great Smoky Mountains National Park. International Ranavirus Symposium, Budapest, Hungary (Oral Presentation).
6.	**Carter ED**. 2017. Gray MJ, Spatz JA, Miller DL, Population Dynamics and Pathogen Prevalence in an Amphibian Breeding Pond in Cades Cove. Great Smoky Mountains National Park Research Colloquium, Gatlinburg, TN (Oral Presentation). 
7.	**Carter ED**. 2017. Gray MJ, Spatz JA, Miller DL, Poor biosecurity could lead to disease outbreaks in amphibian populations. Southeast Partners in Amphibian and Reptile Conservation, Little Rock, Arkansas (Poster).
8.	**Carter ED**. 2017, Amphibian Disease Overview. University of Tennessee-Knoxville Student Chapter of the WDA, Knoxville, Tennessee (Oral Presentation)
9.	**Carter ED**, Gray MJ, Miller DL. 2016. Identifying factors responsible for ranaviral disease outbreaks in Great Smoky Mountains National Park. FWF Graduate Seminar University of Tennessee, Knoxville, TN (Oral Presentation).
10.	**Carter ED**, Gray MJ, Miller DL, Spatz JA, Howard J. 2016. Pathogens vs. pesticides: The threat to eastern hellbenders. Tennessee Wildlife Society, Burns, TN (Oral Presentation).
11.	**Carter ED**, Gray MJ, Miller DL, Spatz JA. 2015. Rapid Transmission of Ranavirus: Role of Direct Contact. Tennessee Herpetology Society, Savannah, TN (Oral Presentation).
12.	**Carter ED**, Goodman RM. 2014. Survey of ranavirus in central Virginia reptiles. Association of Southeastern Biologists, Chattanooga, TN (Poster).
13.	**Carter ED**, Goodman RM. 2014. Survey of ranavirus in central Virginia reptiles. Sigma Xi Research Symposium, Longwood University, VA (Poster).
14.	**Carter ED**, Goodman RM, Hargadon KM. 2014. Survey of ranavirus in central Virginia reptiles. Ecological Society of America annual meeting, Sacramento, CA (Poster).
15.	**Carter ED**, Goodman RM. 2013. Survey of Herpetofauna and Ranavirus on Hampden-Sydney College campus. Sigma Xi Research Symposium, Hampden-Sydney College, VA (Poster).
16.	**Carter ED**, Goodman RM. 2013. Survey of Herpetofauna and Ranavirus on Hampden-Sydney College campus. Sigma Xi Student Research Conference, Research Triangle, NC (Poster).
17.	**Carter ED**, Goodman RM. 2013. Survey of Herpetofauna and Ranavirus on Hampden-Sydney College campus. Virginia Herpetological Society annual meeting, Richmond, VA (Poster). 




```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
