---
title: "Publications and Presentations"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## **Publications**

**PUBLISHED:** 
1.	Gray MJ, Spatz JA, **Carter ED**, Miller DL. Poor Biosecurity Could Lead to Disease Outbreaks in Animal Populations. 2018. PLoS ONE (in press). 
2.	Goodman RM. **Carter ED**. 2017. Survey of Hepetofauna on the Campus of Hampden-Sydney Collece Prince Edward County, Virginia. Catesbeiana 32:2
3.	**Carter ED**. Goodman RM. 2014. Storeria dekayi dekayi (Northern Brown Snake). County record. Catesbeiana 34:1.

**IN REVIEW:**
1.	Goodman RM. **Carter ED**, Hargadon KM. Infection of Ranavirus in Eastern Fence Lizards and Eastern Box Turtles in Central Virginia. Northeastern Naturalist. 
2.	Cusaac JPW, **Carter ED**, Woodhams DC, Robert J, Spatz JA, Howard JL, Lillard C, Graham AW, Hill RD, Reinsch S, McGinnity D, Reeves B, Bemis D, Wilkes RP, Hopkins WB, Waltzek TB, Miller DL, Gray MJ. Interactive Effects of Herbicide and Emerging Amphibian Pathogens in Eastern Hellbender. EcoHealth.
3.	Peace A, O’Regan SM, Spatz JA, Reilly PN, Hill RD, **Carter ED**, Wilkes RP, Waltzek TB, Miller DL, Gray MJ. Dominant transmission pathways depend on population size for a highly virulent, chimeric pathogen. Oikos.

**IN PREPARATION:**
1.	Drought and ranavirus interact to negatively impact wood frogs in the Great Smoky Mountains National Park. Target Journal =  Copeia.
2.	Tolerance of North American Amphibian Species to Batrachochytrium salamandrivorans infections.  Target journal = Proceedings of the National Academy of Sciences (USA). 
3.	Conservation risk of Batrachochytrium salamandrivorans to endemic brook salamanders. Target Journal = Conservation Biology. 
4.	Potential Role of North American Newt Species in the emergence of Batrachochytrium salamandrivorans. Target Journal = Nature. 
5.	Estimating Batrachochytrium salamandrivorans zoospore viability using flow cytometry. Target Journal = Diseases of Aquatic Organisms. 

##**Presentations**

**Lead Presenter:**

1.	**Carter ED**, Gray MJ, Spatz JA, Miller DL. 2018. Interaction of hydroperiod and ranavirus leading to possible amphibian population declines in Great Smoky Mountains National Park. Southeast Partners in Amphibian and Reptile Conservation Helen, GA. (Oral Presentation).
2.	**Carter ED**, Gray MJ, Spatz JA, Miller DL. 2017. Interaction of hydroperiod and ranavirus leading to possible amphibian population declines in Great Smoky Mountains National Park. Southeastern Association of Fish and Wildlife Agencies Louisville, KY (Oral Presentation).
3.	**Carter ED**. 2017. Conservation risk of Batrachochytrium salamandrivorans to endemic brook salamanders. Northeast Partners in Amphibian and Reptile Conservation, Pembroke, VA (Poster).
4.	**Carter ED**. 2017. Gray MJ, Spatz JA, Miller DL, Interaction of hydroperiod and ranavirus leading to possible amphibian population declines in Great Smoky Mountains National Park. Northeast Partners in Amphibian and Reptile Conservation, Pembroke, VA (Poster).
5.	**Carter ED**. 2017. Gray MJ, Spatz JA, Miller DL, Interaction of hydroperiod and ranavirus leading to possible amphibian population declines in Great Smoky Mountains National Park. International Ranavirus Symposium, Budapest, Hungary (Oral Presentation).
6.	**Carter ED**. 2017. Gray MJ, Spatz JA, Miller DL, Population Dynamics and Pathogen Prevalence in an Amphibian Breeding Pond in Cades Cove. Great Smoky Mountains National Park Research Colloquium, Gatlinburg, TN (Oral Presentation). 
7.	**Carter ED**. 2017. Gray MJ, Spatz JA, Miller DL, Poor biosecurity could lead to disease outbreaks in amphibian populations. Southeast Partners in Amphibian and Reptile Conservation, Little Rock, Arkansas (Poster).
8.	**Carter ED**. 2017, Amphibian Disease Overview. University of Tennessee-Knoxville Student Chapter of the WDA, Knoxville, Tennessee (Oral Presentation)
9.	**Carter ED**, Gray MJ, Miller DL. 2016. Identifying factors responsible for ranaviral disease outbreaks in Great Smoky Mountains National Park. FWF Graduate Seminar University of Tennessee, Knoxville, TN (Oral Presentation).
10.	**Carter ED**, Gray MJ, Miller DL, Spatz JA, Howard J. 2016. Pathogens vs. pesticides: The threat to eastern hellbenders. Tennessee Wildlife Society, Burns, TN (Oral Presentation).
11.	**Carter ED**, Gray MJ, Miller DL, Spatz JA. 2015. Rapid Transmission of Ranavirus: Role of Direct Contact. Tennessee Herpetology Society, Savannah, TN (Oral Presentation).
12.	**Carter ED**, Goodman RM. 2014. Survey of ranavirus in central Virginia reptiles. Association of Southeastern Biologists, Chattanooga, TN (Poster).
13.	**Carter ED**, Goodman RM. 2014. Survey of ranavirus in central Virginia reptiles. Sigma Xi Research Symposium, Longwood University, VA (Poster).
14.	**Carter ED**, Goodman RM, Hargadon KM. 2014. Survey of ranavirus in central Virginia reptiles. Ecological Society of America annual meeting, Sacramento, CA (Poster).
15.	**Carter ED**, Goodman RM. 2013. Survey of Herpetofauna and Ranavirus on Hampden-Sydney College campus. Sigma Xi Research Symposium, Hampden-Sydney College, VA (Poster).
16.	**Carter ED**, Goodman RM. 2013. Survey of Herpetofauna and Ranavirus on Hampden-Sydney College campus. Sigma Xi Student Research Conference, Research Triangle, NC (Poster).
17.	**Carter ED**, Goodman RM. 2013. Survey of Herpetofauna and Ranavirus on Hampden-Sydney College campus. Virginia Herpetological Society annual meeting, Richmond, VA (Poster). 

**As Collaborator:**
1.	Gray, M. J., J. P. W. Cusaac, **E. D. Carter**, J. A. Spatz, D. C. Woodhams, L. Rollins-Smith, L. Reinert, L. A. Williams, B. Reeves, P. Nanjappa, and D. L. Miller. 2017. A newly discovered pathogen threatens amphibian biodiversity in the USA. 71st Annual Conference of the Southeastern Association of Fish and Wildlife Agencies, Louisville, KY. (Oral Presentation).
2.	Cusaac, J. P. W., **E. D. Carter**, D. C. Woodhams, A. Peace, L. Rollins-Smith, L. Reinert, L. A. Williams, B. Reeves, P. Nanjappa, C. Richards-Zawacki, D. L. Miller, and M. J. Gray. 2017. Susceptibility of North American Newt Species to Batrachochytrium salamandrivorans. 71st Annual Conference of the Southeastern Association of Fish and Wildlife Agencies, Louisville, KY. (Oral Presentation).
3.	Cusaac, J. P. W., **E. D. Carter**, L. Rollins-Smith, L. Reinert, D. C. Woodhams, C. Richards-Zawacki, D. L. Miller, and M. J. Gray. 2017. Susceptibility of North American Newt Species to Batrachochytrium salamandrivorans. Annual Meeting of the Northeast Partners in Amphibian and Reptile Conservation, Pembroke, VA. (Poster).
4.	Miller, D. L., **E. D. Carter**, J. P. W. Cusaac, R. H. Hardman, L. K. Reinert, L. A. Williams, L. Rollins-Smith, and M. J. Gray. 2017. Batrachochytrium salamandrivorans pathology in susceptible species. 66th Annual International Conference of the Wildlife Disease Association, San Cristobal, Chiapas, Mexico. (Oral Presentation).
5.	Gray, M. J., J. A. Spatz, **E. D. Carter**, and D. L. Miller. 2017. Poor biosecurity could lead to ranavirus outbreaks in amphibian populations. Fourth International Symposium on Ranaviruses, Budapest, Hungary. (Oral Presentation).
6.	Peace, A., S. M. O’Regan, J. A. Spatz, P. N. Reilly, R. D. Hill, **E. D. Carter**, R. P. Wilkes, D. L. Miller, and M. J. Gray. 2017. Incubation delay and multiple infection stages play an important role in Ranavirus disease dynamics. Fourth International Symposium on Ranaviruses, Budapest, Hungary. (Oral Presentation).
7.	Becares, E., M. J. Gray, **E. D. Carter**, I. Fernandez, A. Balseiro, E. R. Gray, and D. L. Miller. 2017. Negative qPCR for Ranavirus, Bd, and Bsal in surveillance samples from Castile and León Province, Spain. Fourth International Symposium on Ranaviruses. Budapest, Hungary. (Poster).
8.	Gray, M. J., **E. D. Carter**, J. A. Spatz, L. K. Reinert, L. Rollins-Smith, and D. L. Miller. 2017. Susceptibility of North American amphibians to the emerging pathogen, Batrachochytrium salamandrivorans. Annual Meeting of the Tennessee Chapter of The Wildlife Society, Paris, TN. (Oral Presentation).
9.	Cusaac, J. P. W., **E. D. Carter**, J. A. Spatz, D. L. Miller, and M. J. Gray. 2017. Invasive Green Tree Frogs (Hyla cinerea) Have the Capability of Translocating an Emerging Pathogen in the Great Smoky Mountains National Park. Great Smoky Mountains National Park Science Colloquium, Gatlinburg, TN. (Oral Presentation).
10.	Gray, M. J., J. A. Spatz, **E. D. Carter**, L. K. Reinert, L. Rollins-Smith, D. L. Miller. 2016. Susceptiblity of North American amphibians to Batrachochytrium salamandrivorans (Bsal). Eighth World Congress of Herpetology, Hangzhou, China. (Oral Presentation).
11.	Gray, M. J., C. E. Lillard, J. L. Howard, J. A. Spatz, **E. D. Carter**, R. P. Wilkes, L. Rollins-Smith, B. Reeves, D. McGinnity, S. Reinsch, and D. L. Miller. 2016. Pathogens vs. Pesticides: What is the greater threat to Eastern Hellbenders? Eighth World Congress of Herpetology, Hangzhou, China. (Oral Presentation).  
12.	Gray, M. J., J. A. Spatz, **E. D. Carter**, and D. L. Miller. 2016. Poor biosecurity could lead to disease outbreaks in amphibian populations. International Conference of the Wildlife Disease Association. Cortland, New York. (Oral Presentation).
13.	Miller, D. L. C. E. Lillard, J. L. Howard, J. A. Spatz, **E. D. Carter**, R. P. Wilkes, L. Rollins-Smith, B. Reeves, D. McGinnity, S. Reinsch, and M. J. Gray. 2016. Role of ranavirus in eastern hellbender declines. International Conference of the Wildlife Disease Association. Cortland, New York. (Oral Presentation).
14.	Gray, M. J., J. Spatz, **E. D. Carter**, and D. L. Miller. 2015. Poor biosecurity could lead to disease outbreaks in amphibian populations. Annual Meeting of the Southeastern Association of Fish and Wildlife Agencies. Asheville, North Carolina. (Oral Presentation).
15.	Spatz, J., M. J. Gray,**E. D. Carter**, and D. L. Miller. 2015. Poor biosecurity could lead to disease outbreaks in amphibian populations. Annual Meeting of the Tennessee Herpetological Society, Savannah, TN. (Oral Presentation).  


```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
